Interoperable

### 2019-11-16 report/cloud-course-final-report/intro.tex
Change minor things in report

Traditional VMs virtualize hardware resources, which results in the VMs taking up more resources. As such, OS-level virtualization, or Containers, have been developed. By sharing OS resources, containers are lightweight and can be spun up quickly while taking up fewer resources. Docker, introduced in 2013, is a popular runtime to manage containers as it addresses end-to-end management. However, Docker was initially a monolith with features not inherently dependent on each other being bundled together. As a result, alternative runtimes such as CRI-O and contianerd exist which implement container management at varying levels. [1]

>>>>

Traditional VMs virtualize hardware resources, which results in the VMs taking up more resources. As such, OS-level virtualization, or Containers, have been developed. By sharing OS resources, containers are lightweight and can be spun up quickly while taking up fewer resources.
Sharing OS resources such as libraries significantly reduces the need to reproduce the operating system code, and means that a server can run multiple workloads with a single operating system installation.
Containers are thus exceptionally light.

Containers are implemented using Linux namespaces and cgroups. \textbf{Namespaces} let you virtualize system resources, like the file system or networking, for each container. \textbf{Cgroups} provide a way to limit the amount of resources like CPU and memory that each container can use.

Docker, introduced in 2013, is a popular runtime to manage containers as it addresses end-to-end management. However, Docker was initially a monolith with features not inherently dependent on each other being bundled together. As a result, alternative runtimes such as CRI-O and contianerd exist which implement container management at varying levels. [1]
